Back to Normal Transits for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-15 ms.tex
specmatch stuff including radius.

>>>>

\subsection{Specmatch}\label{sec:SpecMatch}

We also use the \texttt{specmatch} tool \citep{yee2017specMatch} to estimate the stellar parameters using the Subaru spectrum.
\texttt{specmatch} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
As with the comparisons to the BOSZ models, we first convolve the median spectrum from \citet{masuda2018rvKIC1255} with a R=40,000 kernel.
We cut the spectrum to a region from 5140~$\AA$ to 5190~$\AA$ to focus on the gravity-sensitive Mg triplet.

Figure \ref{fig:specMatch} shows the chi-squared differences between the median Subaru spectrum and the models.
The effective temperature radius show clear global $\chi^2$ minima for the HIRES spectral libraries.
The resulting best-fit parameters are T$_{eff}$=4500 K, [Fe/H]=-0.1$\pm$0.1, log(g)=4.5$\pm$0.1, R=0.7 $\pm$ 0.1 R$_\odot$.
We summarize these \texttt{specmatch} and BOSZ results in Table \ref{tab:stellObsParams}.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/subaru/spec_chi_min.pdf}
\caption{$\chi^2$ as a function of stellar parameters found by \texttt{specmatch}.
The effective temperature and radii show clear global minima.}\label{fig:specMatch}
\end{centering}
\end{figure*}
